Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-13 Paper.Rmd
adding response

\begin{figure}[!h]
\textbf{ \hspace{6 cm} (A) \hspace{6 cm} (B)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf}\\
\end{center}
\vspace{0.2 cm}
\textbf{ \hspace{6 cm} (C) \hspace{6 cm} (D)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf}
\caption{Skewness of spatially averaged green spruce aphid abundance $(A)$, leaf-curling plum 
aphid first flight dates $(B)$, \emph{Ceratium furca} abundance $(C)$, and methane-flux
$(D)$ time series compared to an multivariate 
N-copula null hypothesis. Black dots are empirical 
skewnesses; see text 
and Appendix \ref{SM-Surrog_multi} for details of the null hypothesis. Results show a 
tendency for skewness of the spatial average to be affected as hypothesized 
by tail dependence. \label{fig_skewness_spearman}}
\end{center}
\end{figure}

@@

```{r read_tl_aphid_count_sp6, echo=F}
tlsp6<-readRDS("./Results/taylorslaw_results/tl_aphid_count_sp6.RDS")
```

Results also suggested that copula structure contributes to the linearity of 
spatial Taylor's law. For instance, the spatial Taylor's law relationship 
for corn leaf aphid abundance data was significantly less curved than for 
surrogate datasets (Fig. \ref{fig_sTL_mncurv_sp6}). Three of $20$ aphid species
had cuvatures less than at least $95\%$ of surrogate datasets ($p=X$, $Y$, $Z$ for 
the $A$, $B$ and $C$ species, respectively). 
<!--***DAN: Shya, please fill in X, Y, Z, A, B, C with autolinks)-->
Three such significant
results of 20 species could have occurred by chance due to 
multiple-testing error. However, for each of the 20 species, we computed the fraction
of surrogate curvatures less than the curvature that came from real data, and we
combined these $p$-values using Fisher's combined probability test to get an
aggregate $p$-value of $0.019$ 
<!--***DAN: Shya, see the Wikipedia article on Fisher's method to learn about it. Then 
you need to put this analysis into the code suite and have the resulting p value
typed in above be an autolink instead. Here is what I did: 
1) I copied by hand all the pleft values on the pdf you sent me into a vector pleft. Instead you should create such a vector in your code from your test output, not typing in the results.
2) I used the formula stat<--2*sum(log(pleft)) to get the Fisher method statistic
3) I compared to a chi-squared distribution with 40 degress of freedom using 1-pchisq(stat,40) to get my p-value
Please let me know if any of this is unclear.-->
for the test of the null hypothesis that 
copula structure did not contribute to linearity of Taylor's law for any of the 
species. This result is usefully suggestive and can guide future work, but still does not
provide certainty, because the Fisher method provides $p$-values that are too 
small if its assumption of independent tests is violated. Though our 20 species
have different host plants so may be independent for the purposes of our analyses, 
it would be difficult to fully assess independence.
<!--***DAN: Shya, can you remind me why the same analyses were not done for plankton,
if there is a good reason? Or if you did it, what were the results?--> 
We provide simulation results in Appendix \ref{SM-Consequence_TL_simulation}
that robustly illustrate, at least in the model setup we used, 
that copula structure influences spatial Taylor's law.

\begin{figure}[!h]
\textbf{ \hspace{4 cm} (A) \hspace{4 cm} (B) \hspace{4 cm} (C)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=10 cm]{./Results/taylorslaw_results/aphid_count_sp6_logv_vs_logm.pdf}
\includegraphics[width=5 cm]{./Results/taylorslaw_results/aphid_count_sp6_sTL_mncurv.pdf}\\
\caption{Mean curvature of the spatial Taylor's law relationship for 
corn leaf aphid abundance
data (A) was significantly less than for surrogates (B, C). The Taylor's law 
relationship for one example surrogate (B) shows shows greater curvature than
for data (A), and the significance of the difference was demonstrated
by the fact that only $39$ of $10000$ surrogates had curvature less than that
of the data (C). See Appendix \ref{SM-TL_curvature} for details on 
how curvature was calculated.\label{fig_sTL_mncurv_sp6}}
\end{center}
\end{figure}
<!--***DAN: Shya, pls make the x axis label on C read simply "Mean curvature"-->

>>>>

\begin{figure}[!h]
\textbf{ \hspace{6.6 cm} (A) \hspace{4.6 cm} (B)} \\
\vspace{-0.4 cm}
\begin{center}
\includegraphics[width=5 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf}
\includegraphics[width=5 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf}\\
\end{center}
\vspace{0.2 cm}
\textbf{ \hspace{6.6 cm} (C) \hspace{4.6 cm} (D)} \\
\vspace{-0.4 cm}
\begin{center}
\includegraphics[width=5 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf}
\includegraphics[width=5 cm]{./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf}
\caption{Skewness of spatially averaged green spruce aphid abundance $(A)$, leaf-curling plum 
aphid first flight dates $(B)$, \emph{Ceratium furca} abundance $(C)$, and methane-flux
$(D)$ time series compared to an multivariate 
N-copula null hypothesis. Black dots are empirical 
skewnesses; see text 
and Appendix \ref{SM-Surrog_multi} for details of the null hypothesis. Results show a 
tendency for skewness of the spatial average to be affected as hypothesized 
by tail dependence. \label{fig_skewness_spearman}}
\end{center}
\end{figure}

@@

```{r read_tl_aphid_count_sp6, echo=F}
tlsp6<-readRDS("./Results/taylorslaw_results/tl_aphid_count_sp6.RDS")
tl_aphid_count<-readRDS("./Results/taylorslaw_results/tl_aphid_count.RDS")
aphid_info<-readRDS("./Results/aphid_info.RDS")
pleft<-tl_aphid_count$p_left_mncurv
stat<--2*sum(log(pleft))
pchi2<-1-pchisq(stat,40)
idsp<-which(pleft<0.05)
pleftgood<-pleft[idsp]
```

Results also suggested that copula structure contributes to the linearity of 
spatial Taylor's law. For instance, the spatial Taylor's law relationship 
for corn leaf aphid abundance data was significantly less curved than for 
surrogate datasets (Fig. \ref{fig_sTL_mncurv_sp6}). Three of $20$ aphid species
had cuvatures less than at least $95\%$ of surrogate datasets ($p=$ `r pleftgood` for 
the `r aphid_info$c1[idsp]` species, respectively). 
<!--***DAN: Shya, please fill in X, Y, Z, A, B, C with autolinks)
***Shya: Done.-->
Three such significant
results of 20 species could have occurred by chance due to 
multiple-testing error. However, for each of the 20 species, we computed the fraction
of surrogate curvatures less than the curvature that came from real data, and we
combined these $p$-values using Fisher's combined probability test to get an
aggregate $p$-value of `r pchi2`
<!--***DAN: Shya, see the Wikipedia article on Fisher's method to learn about it. Then 
you need to put this analysis into the code suite and have the resulting p value
typed in above be an autolink instead. Here is what I did: 
1) I copied by hand all the pleft values on the pdf you sent me into a vector pleft. Instead you should create such a vector in your code from your test output, not typing in the results.
2) I used the formula stat<--2*sum(log(pleft)) to get the Fisher method statistic
3) I compared to a chi-squared distribution with 40 degress of freedom using 1-pchisq(stat,40) to get my p-value
Please let me know if any of this is unclear.
***Shya: Done.-->
for the test of the null hypothesis that 
copula structure did not contribute to linearity of Taylor's law for any of the 
species. This result is usefully suggestive and can guide future work, but still does not
provide certainty, because the Fisher method provides $p$-values that are too 
small if its assumption of independent tests is violated. Though our 20 species
have different host plants so may be independent for the purposes of our analyses, 
it would be difficult to fully assess independence.
<!--***DAN: Shya, can you remind me why the same analyses were not done for plankton,
if there is a good reason? Or if you did it, what were the results?
***Shya : we did it, I have the pdf but I don't have the code where I called to generate the pdf,
As we could not get any significant results for a single species (see attachment in the mail I sent you)
we did not show the results.--> 
We provide simulation results in Appendix \ref{SM-Consequence_TL_simulation}
that robustly illustrate, at least in the model setup we used, 
that copula structure influences spatial Taylor's law.

\begin{figure}[!h]
\textbf{ \hspace{4 cm} (A) \hspace{4 cm} (B) \hspace{4 cm} (C)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=10 cm]{./Results/taylorslaw_results/aphid_count_sp6_logv_vs_logm.pdf}
\includegraphics[width=5 cm]{./Results/taylorslaw_results/aphid_count_sp6_sTL_mncurv.pdf}\\
\caption{Mean curvature of the spatial Taylor's law relationship for 
corn leaf aphid abundance
data (A) was significantly less than for surrogates (B, C). The Taylor's law 
relationship for one example surrogate (B) shows shows greater curvature than
for data (A), and the significance of the difference was demonstrated
by the fact that only `r (tlsp6$p_left_mncurv)*10000` of $10000$ surrogates had curvature less than that
of the data (C). See Appendix \ref{SM-TL_curvature} for details on 
how curvature was calculated.\label{fig_sTL_mncurv_sp6}}
\end{center}
\end{figure}
<!--***DAN: Shya, pls make the x axis label on C read simply "Mean curvature"
***sHYA: dONE.-->

### 2019-02-13 SupportingInformation.Rmd
adding response

knitr::kable(aphid_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 20 aphids for which data were available \\label{tab_aphid_info}",
      col.names = NULL)%>%
     column_spec(column = 2,italic=T)%>%add_header_above(header=c("Common name" = 1, "Latin binomial" = 1))
```

@@

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman") 
hist(answer1s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer1s$realskw,y=0,col="black",pch=15,cex=2)

@@

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer2s<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman")
hist(answer2s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer2s$realskw,y=0,col="black",pch=15,cex=2)

@@

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer3s<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman") 
hist(answer3s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer3s$realskw,y=0,col="black",pch=15,cex=2)

@@

pdf("./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=F,
                           corpres="spearman") 
hist(answer1s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer1s$realskw,y=0,col="black",pch=15,cex=2)

@@

#call on real data
# For all sp
splist<-c(1:20)
tl_aphid_count<-as.data.frame(matrix(NA,nrow=length(splist),ncol=10))
colnames(tl_aphid_count)<-c("real_sTL_slope","p_left","p_right","numsurrog_good",
                            "real_sTL_quadcoeff","p_left_quadcoeff","p_right_quadcoeff",
                            "real_sTL_mncurv","p_left_mncurv","p_right_mncurv")
rownames(tl_aphid_count)<-paste("sp",splist,sep="")
#pdf("aphid_count_allsp_spTLslope.pdf",height=20,width=20)
#pdf("./Results/taylorslaw_results/aphid_count_allsp_sTL_quadcoeff.pdf",height=20,width=20)
pdf("./Results/taylorslaw_results/aphid_count_allsp_sTL_mncurv.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
for(i in splist){
  #cat("sp=",i,"\n")
  #ans<-TL_on_realdata(data=data_aphid_count,numsurrog=10000,sp=i,data_pt_thrs = 30,ploton=T,tag="slope",labelon=T)
  #ans<-TL_on_realdata(data=data_aphid_count,numsurrog=10000,sp=i,data_pt_thrs = 30,ploton=T,tag="quadcoeff",labelon=T)
  ans<-TL_on_realdata(data=data_aphid_count,numsurrog=10000,sp=i,data_pt_thrs = 30,ploton=T,tag="mncurv",labelon=T)
  tl_aphid_count$real_sTL_slope[i]<-ans$real_spatialTLslope
  tl_aphid_count$p_left[i]<-ans$p_left
  tl_aphid_count$p_right[i]<-ans$p_right
  tl_aphid_count$numsurrog_good[i]<-ans$numsurrog_good
  tl_aphid_count$real_sTL_quadcoeff[i]<-ans$real_sTL_quadcoeff
  tl_aphid_count$p_left_quadcoeff[i]<-ans$p_left_quadcoeff
  tl_aphid_count$p_right_quadcoeff[i]<-ans$p_right_quadcoeff
  tl_aphid_count$real_sTL_mncurv[i]<-ans$real_sTL_mncurv
  tl_aphid_count$p_left_mncurv[i]<-ans$p_left_mncurv
  tl_aphid_count$p_right_mncurv[i]<-ans$p_right_mncurv
}
par(op)
dev.off()
saveRDS(tl_aphid_count,"./Results/taylorslaw_results/tl_aphid_count.RDS")
```

```{r spatialTL_on_realdata_aphid_count_sp6, results="hide", echo=F, cache=T, cache.extra=list(seed,data_aphid_count,TL_on_realdata,mtime("good_loclist.R"),mtime("TaylorsLawTools.R"),mtime("mncurvat.R"),mtime("ncsurrog.R"))}

set.seed(seed)

#Now for sp=6
sp<-6
pdf("./Results/taylorslaw_results/aphid_count_sp6_sTL_mncurv.pdf",height=5,width=5)
op<-par(mar=c(4,5,1,1),mgp=c(3,1,0))
ans<-TL_on_realdata(data=data_aphid_count,numsurrog=10000,sp=sp,data_pt_thrs = 30,ploton=T,tag="mncurv",labelon = F)
saveRDS(ans,"./Results/taylorslaw_results/tl_aphid_count_sp6.RDS")
mtext(paste0("p= ",ans$p_left_mncurv),side = 3, line=-2, adj=0.5, col="black",cex=2)
par(op)
dev.off()

pdf("./Results/taylorslaw_results/aphid_count_sp6_logv_vs_logm.pdf",height=5,width=10)
op<-op<-par(mfrow=c(1,2),mar=c(4,5,1,1),mgp=c(3,1,0))
plot(ans$realTL_stats$s.points,xlab=expression(log[10]("spatial mean")),
     ylab=expression(log[10]("spatial variance")),col="black",
     cex.axis=1.5,cex.lab=1.5)
mtext(paste0("mean curvature= ",round(unname(ans$realTL_stats$s.stats[7]),3)),side = 3, line=-2, adj=0, col="black",cex=2)

target_mncurv<-0.1
id<-which(abs(ans$good_surrog_mncurv-target_mncurv)<1e-4)[1]
ans_s<-ans$surrogTL_stats
plot(ans_s[[id]]$s.points,xlab=expression(log[10]("spatial mean")),
     ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)
mtext(paste0("mean curvature= ",round(ans$good_surrog_mncurv[id],3)),side = 3, line=-2, adj=0, col="black",cex=2)

@@

<!--***DAN: Shya, I need a reminder how we did this, can you please tell me where the
code is, then I can write this section. Feel free to take a stab at it yourself, too,
though.-->

>>>>

saveRDS(aphid_info,"./Results/aphid_info.RDS")
knitr::kable(aphid_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 20 aphids for which data were available \\label{tab_aphid_info}",
      col.names = NULL)%>%
     column_spec(column = 2,italic=T)%>%add_header_above(header=c("Common name" = 1, "Latin binomial" = 1))
```

@@

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf",height=5,width=5)
op<-par(mar=c(4,5,1,1),mgp=c(3,1,0))
#op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman") 
hist(answer1s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer1s$realskw,y=0,col="black",pch=15,cex=2)

@@

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf",height=5,width=5)
op<-par(mar=c(4,5,1,1),mgp=c(3,1,0))
answer2s<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman")
hist(answer2s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer2s$realskw,y=0,col="black",pch=15,cex=2)

@@

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf",height=5,width=5)
op<-par(mar=c(4,5,1,1),mgp=c(3,1,0))
answer3s<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman") 
hist(answer3s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer3s$realskw,y=0,col="black",pch=15,cex=2)

@@

pdf("./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf",height=5,width=5)
op<-par(mar=c(4,5,1,1),mgp=c(3,1,0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=F,
                           corpres="spearman") 
hist(answer1s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer1s$realskw,y=0,col="black",pch=15,cex=2)

@@

#call on real data
# For all sp
splist<-c(1:20)
tl_aphid_count<-as.data.frame(matrix(NA,nrow=length(splist),ncol=10))
colnames(tl_aphid_count)<-c("real_sTL_slope","p_left","p_right","numsurrog_good",
                            "real_sTL_quadcoeff","p_left_quadcoeff","p_right_quadcoeff",
                            "real_sTL_mncurv","p_left_mncurv","p_right_mncurv")
rownames(tl_aphid_count)<-paste("sp",splist,sep="")
#pdf("aphid_count_allsp_spTLslope.pdf",height=20,width=20)
#pdf("./Results/taylorslaw_results/aphid_count_allsp_sTL_quadcoeff.pdf",height=20,width=20)
pdf("./Results/taylorslaw_results/aphid_count_allsp_sTL_mncurv.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
for(i in splist){
  #cat("sp=",i,"\n")
  #ans<-TL_on_realdata(data=data_aphid_count,numsurrog=10000,sp=i,data_pt_thrs = 30,ploton=T,tag="slope",labelon=T)
  #ans<-TL_on_realdata(data=data_aphid_count,numsurrog=10000,sp=i,data_pt_thrs = 30,ploton=T,tag="quadcoeff",labelon=T)
  ans<-TL_on_realdata(data=data_aphid_count,numsurrog=10000,sp=i,data_pt_thrs = 30,ploton=T,tag="mncurv",labelon=T)
  if(i==6){
    saveRDS(ans,"./Results/taylorslaw_results/tl_aphid_count_sp6.RDS") #saving sp=6 results
  }
  tl_aphid_count$real_sTL_slope[i]<-ans$real_spatialTLslope
  tl_aphid_count$p_left[i]<-ans$p_left
  tl_aphid_count$p_right[i]<-ans$p_right
  tl_aphid_count$numsurrog_good[i]<-ans$numsurrog_good
  tl_aphid_count$real_sTL_quadcoeff[i]<-ans$real_sTL_quadcoeff
  tl_aphid_count$p_left_quadcoeff[i]<-ans$p_left_quadcoeff
  tl_aphid_count$p_right_quadcoeff[i]<-ans$p_right_quadcoeff
  tl_aphid_count$real_sTL_mncurv[i]<-ans$real_sTL_mncurv
  tl_aphid_count$p_left_mncurv[i]<-ans$p_left_mncurv
  tl_aphid_count$p_right_mncurv[i]<-ans$p_right_mncurv
}
par(op)
dev.off()
saveRDS(tl_aphid_count,"./Results/taylorslaw_results/tl_aphid_count.RDS")
```

```{r spatialTL_on_realdata_aphid_count_sp6, results="hide", echo=F}
#Now for sp=6

ans<-readRDS("./Results/taylorslaw_results/tl_aphid_count_sp6.RDS")

pdf("./Results/taylorslaw_results/aphid_count_sp6_sTL_mncurv.pdf",height=5,width=5)
op<-par(mar=c(4,5,1,1),mgp=c(3,1,0))
hist(ans$good_surrog_mncurv,breaks=100,main="",xlab="Mean curvature",cex.axis=2,cex.lab=2,cex=2,col="grey",border=F)
points(x=ans$real_sTL_mncurv,y=0,col="black",pch=15,cex=2)
mtext(paste0("p= ",ans$p_left_mncurv),side = 3, line=-2, adj=0.5, col="black",cex=2)
par(op)
dev.off()

pdf("./Results/taylorslaw_results/aphid_count_sp6_logv_vs_logm.pdf",height=5,width=10)
op<-par(mfrow=c(1,2),mar=c(4,5,1,1),mgp=c(3,1,0))
plot(ans$realTL_stats$s.points,xlab=expression(log[10]("spatial mean")),
     ylab=expression(log[10]("spatial variance")),col="grey",pch=20,cex=1.5,
     cex.axis=2,cex.lab=2)
mtext(paste0("mean curvature= ",round(unname(ans$realTL_stats$s.stats[7]),3)),side = 3, line=-2, adj=0, col="black",cex=2)

target_mncurv<-0.1
id<-which(abs(ans$good_surrog_mncurv-target_mncurv)<1e-4)[1]
ans_s<-ans$surrogTL_stats
plot(ans_s[[id]]$s.points,xlab=expression(log[10]("spatial mean")),
     ylab=expression(log[10]("spatial variance")),col="grey",pch=20,cex=1.5,
     cex.axis=2,cex.lab=2)
mtext(paste0("mean curvature= ",round(ans$good_surrog_mncurv[id],3)),side = 3, line=-2, adj=0, col="black",cex=2)

@@

<!--***DAN: Shya, I need a reminder how we did this, can you please tell me where the
code is, then I can write this section. Feel free to take a stab at it yourself, too,
though.
***Shya: What do you want to know? how did you calculate mean curvature and 
slope for made up data or you want to see code with real data?

In case of made up data :
For each non-N copula family (C,F,SC) you generated surrogates
having similar correlation (spearman/ kendall, though for 
consistency we added plots in suppmat with spearman) that of N copula
[using copsurrognd.R] : this thing is done in r chunk named "taylors_law_make_surrogs".

Then you did spatial-TL calculation for each set of copula family in r chunk "tl_analysis"
[using TaylorsLawTools.R which calls mncurvat.R code to calculate mean curvature]

Next two r chunks : taylor_plots_kendall and taylor_plots_spearman generates plot with those data.

For spatial TL calculation on real data :

We used Aphid count all sp with spearman only, but to show a plot for example chose sp=6 (corn leaf aphid)
as it had significant p_left value for mean curvature.
code is in r chunk named "spatialTL_on_realdata_aphid_count".
-->
